---
title: "Mini-Project 2"
author: "Guadalupe Chimil, Annah Lee, Ivette Viramontes"
date: "March 22, 2018"
output: html_document
---

## Loading the data
```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
load("individuals.rda") 
```

```{r}
library(individuals)
Women<-individuals %>%
  
  filter(cmte_id=="C00283432"| cmte_id=="C00530766") 
  filter(cmte_id == "C00473918"| 
         cmte_id == "C00530766",
         transaction_dt <= "11062012",
         entity_type == "IND")
         transaction_dt >= "01012012" & 
         transaction_dt <= "12312012"
         entity_type == "IND") 

Donations<- contributions %>%
  filter(cmte_id == "C00473918"| 
         cmte_id == "C00530766",
         transaction_type == "24E")

NatComm <- individuals %>%
  filter(transaction_type == "11") %>% 
  full_join(x = NativeAmerican, y = committees, by="cmte_id") 

  select(-amndt_ind, -rpt_type) %>%
  select( -transaction_pgi, -image_num) %>%
  select( -city, -state) %>%
  select( -zip_code, -employer) %>%
  select( -occupation, -other_id) %>%
  select( -tran_id, -file_num) %>% 
  select( -memo_cd, -memo_text, -sub_id)
  
NatComm2 <- individuals %>%
  full_join(x=individuals, y=committees, by="cmte_id") %>%
  filter(transaction_type == "11", 
         entity_type == "ORG",
         transaction_pgi == "G") %>% 
  select(-amndt_ind, 
         -rpt_type, 
         -image_num, 
         -city, 
         -state, 
         -zip_code, 
         -employer,
         -occupation, 
         -other_id, 
         -tran_id, 
         -file_num, 
         -memo_cd, 
         -memo_text, 
         -sub_id, 
         -tres_name, 
         -cmte_st1, 
         -cmte_st2, 
         -cmte_city, 
         -cmte_state,
         -cmte_zip,
         -cmte_dsgn,
         -cmte_filing_freq,
         -connected_org_name,
         -org_type,
         -cand_id) 

```

join from candidates data the candidate name that identifies the cand_id number

Women Vote and Women SpeaK Out (ProChoice & ProLife) 
Individuals that donate to their PAC
How much did an individual donate to a committee (WV and WSO) in the year 2012?

filter(cmte_id == "C00473918"| 
         cmte_id == "C00530766")

```{r}
  
  select(-amndt_ind, -rpt_type) %>%
  select( -transaction_pgi, -image_num) %>%
  select( -city, -state) %>%
  select( -zip_code, -employer) %>%
  select( -occupation, -other_id) %>%
  select( -tran_id, -file_num) %>% 
  select( -memo_cd, -memo_text, -sub_id) 
```  



```{r}
#install.packages("lubricate")  
#library(lubridate)  
#Native_Committees %>% 
  #select(transaction_dt) %>% 
  #filter(transaction_dt >= date("01012012") & transaction_dt <= date("12312012")) 

Native_Commit %>% individuals %>%
  full_join(x=NativeAmerican, y=committees, by="NACommit") 